Political Support in the United States

### 2024-03-17 paper/paper.qmd
Update paper.qmd

Based on the analysis of Figure 1, located under 2.3 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2). Throughout most of the race, 1 consistently has fewer votes than 2. Specifically, women are identified as the demographic most inclined to vote for Biden, indicating a notable gender disparity in political preferences favoring the Biden candidacy. This trend is very recognizable based on research @Misc: women are registered to vote in the U.S. at higher rates than men. In recent years, the number of women registered to vote in the U.S. has typically been about 10 million more than the number of men registered to vote. In every presidential election since 1980, the proportion of eligible female adults who voted has exceeded the proportion of eligible male adults who voted. In all presidential elections prior to 1980, the voter turnout rate for women was lower than the rate for men. The number of female voters has exceeded the number of male voters in every presidential election since 1964.

@@

Based on the analysis of Figure 1, located under 2.3 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden. In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races. For example, Black individuals have a total vote of 5293 individuals for Biden, however only 642 individuals support and vote for Trump. This same trend can also be observed in races such as Middle Eastern, Hispanic, Black and Asian individuals. Additionally, in recent elections @Misc, among Asian American/Pacific Islander, Black, Hispanic, and white voters, the number of women voters has exceeded the number of male voters. The gender gap in voter turnout rates is the largest for Black voters. Women have also voted at higher rates than men among Hispanic and white voters in all presidential elections since the 1980s. Among Asian American/Pacific Islander voters, there is no consistent gender gap in voter turnout.

>>>>

Based on the analysis of Figure 1, located under 2.3 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2). Throughout most of the race, 1 consistently has fewer votes than 2. Specifically, women are identified as the demographic most inclined to vote for Biden, indicating a notable gender disparity in political preferences favoring the Biden candidacy. This trend is very recognizable based on research: women are registered to vote in the U.S. at higher rates than men. In recent years, the number of women registered to vote in the U.S. has typically been about 10 million more than the number of men registered to vote. In every presidential election since 1980, the proportion of eligible female adults who voted has exceeded the proportion of eligible male adults who voted. In all presidential elections prior to 1980, the voter turnout rate for women was lower than the rate for men. The number of female voters has exceeded the number of male voters in every presidential election since 1964.

@@

Based on the analysis of Figure 1, located under 2.3 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden. In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races. For example, Black individuals have a total vote of 5293 individuals for Biden, however only 642 individuals support and vote for Trump. This same trend can also be observed in races such as Middle Eastern, Hispanic, Black and Asian individuals. Additionally, in recent elections, among Asian American/Pacific Islander, Black, Hispanic, and white voters, the number of women voters has exceeded the number of male voters. The gender gap in voter turnout rates is the largest for Black voters. Women have also voted at higher rates than men among Hispanic and white voters in all presidential elections since the 1980s. Among Asian American/Pacific Islander voters, there is no consistent gender gap in voter turnout.
